US President Prediction

### 2024-11-03 paper/paper.qmd
update survey

We use the statistical programming language R [@citeR].... Our data.... Following @tellingstories, we consider...

@@

3. Who would you vote for?

* Donald Trump - Republican
* Kamala Harris - Democrat
* Other Candidates
* Not Decided Yet

@@

5. How likely are you to vote for the election?

* Very Likely
* A Bit Likely
* Not Likely

@@

7. sex

8. race

9. education

10. How many characters are present in the word "President"?

>>>>

cite R, packages, dataa
The data used in this paper is source from FiveThirtyEight ("538presidentialpolls", 2024). T
We use the statistical programming language R [@citeR].... Our data.... Following @tellingstories, we consider...

@@

3. If the election were held today, who would you most likely vote for?

* Donald Trump - Republican
* Kamala Harris - Democrat
* Other Candidates
* Not Decided Yet
* Prefer not to say

@@

5. How many characters are present in the word "President"?

@@

7. What is your sex?

* Male
* Female
* Non-binary
* Prefer not to say

8. What is your Ethnity/Race?

* White
* Black or African American
* Hispanic or Latino
* Asian
* Native American or Alaska Native
* Native Hawaiian or Other Pacific Islander
* Middle Eastern or North African
* Prefer not to say
* Other (please specify) [optional text box]

9. What is your Education Level?

* Less than high school
* High school diploma or equivalent
* Some college, no degree
* Associate’s degree
* Bachelor’s degree
* Master’s degree
* Professional or doctoral degree (JD, MD, PhD, etc.)
* Prefer not to say

10.How do you plan to vote?

* In-person on Election Day
* In-person early voting
* Mail-in/Absentee ballot
* Undecided

11. Is there anything else you’d like to share about your voting decision or concerns?
